Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-30 draft/ms_v5.tex
Minor changes

    At \s2n{}$=5$, HSC Wide can detect stars as faint as ${\sim}26.5$ mag in both $g$ 
    and $i$ bands, which is consistent with the values found in \citet{HSCDR1} for 
    average seeing conditions.
    However, it is worth reminding HSC data users that the detection
    limit will exhibit spatial variations due to the seeing conditions.

@@

    We now investigate the performance of the PSF photometry in each of the five bands
    independently. 
    Fig \ref{fig:psf_mag} shows the difference between the input magnitude versus the
    \hscpipe{} \forced{} PSF magnitude ($\Delta \mathrm{mag}_{\mathrm{PSF}}$) as a 
    function of input magnitude. 
    We separate these stars into seven input magnitude bins.  
    In each bin, we characterize the statistical \textbf{precision} of the PSF 
    magnitude using the standard deviation of the $\Delta \mathrm{mag}_{\mathrm{PSF}}$ 
    distribution.
    Meanwhile, we characterize the statistical \textbf{accuracy} of the PSF magnitude 
    via the mean magnitude difference in each bin. 
    This also informs us whether the PSF photometry is biased at certain input 
    magnitude.

@@

	Finally, we also perform similar tests for the \unforced{} PSF photometry in all 
	five bands, and find similar results. 
	To measure the \forced{} PSF photometry, \hscpipe{} fixes the centroid of the PSF 
	model across all five bands. 
	A difference between \forced{} and \unforced{} PSF magnitudes would therefore be 
	an indication of photometric uncertainties arising from inaccurate astrometric 
	calibrations and PSF modeling across different bands\footnote{On average, the 
	centroids are more accurate in \forced{} photometry as they are defined using 
	the band with higher \s2n{}}. 
	Fig \ref{fig:psf_diff} shows the difference between \forced{} and \unforced{} 
	PSF photometry for the $g$ and the $y$ band. 
	The overall differences are small ($<0.01$ mag). 
	At very faint end ($g_{\mathrm{Input}}>24.0$ mag and $g_{\mathrm{Input}}>23.5$

@@

    The typical precision of $i$-band flux using \forced{} \cmodel{} is at 
    ${\sim}7-9$\% level in the \texttt{goodSeeing} \tract{} at 
    $i_{\mathrm{Input}}<24.0$ mag. 
    It moderately degrades to ${\sim}11$\% at $25.0$ mag. 
    The performance is similar in $i$ band for the \texttt{badSeeing} \tract{}. 
    At $20.0 < i_{\mathrm{Input}} < 25.0$ mag, the accuracies of \forced{} \cmodel{}
    magnitudes change from \plus{}$0.041$ mag to \minus{}$0.005$ mag, which suggest
    that \forced{} \cmodel{} photometry is unbiased down to the very faint end.

@@

    The precision of \forced{} \cmodel{} photometry is consistent across all filters.
    For the $g$, $r$, and $z$ bands, the statistical uncertainties are very similar to
    $i$-band results between $20.0$ and $25.0$ mag.
    The \forced{} \cmodel{} magnitudes are also unbiased for these three filters
    across the entire input magnitude range.
    The precision for the $y$ band is slightly worse, ranging from 9\% to 17\% in the
    same magnitude bins.
    In addition, the \forced{} \cmodel{} tends to overestimate the total flux in 
    the $y$ band at $>24.0$ mag. 
    This bias in the $y$ band flux is equal to \minus{}0.06 at $24.0$ mag to 
    \minus{}0.22 mag at 25.0 mag. 
    Worse seeing conditions and a higher background noise level mean that it is more
    difficult to detect faint objects in the $y$ band.
    At $y_{\mathrm{Input}}{\sim}24.0$, the average \s2n{} for \cmodel{} is already
    around the detection threshold.

>>>>

    At \s2n{}$=5$, HSC Wide can detect stars as faint as ${\sim}26.5$ mag in both $g$ 
    and $i$ bands, which is consistent with the values found in \citet{HSCDR1} for 
    average seeing conditions.
    However, it is worth reminding HSC data users that the detection
    limit will exhibit spatial variations due to the seeing conditions.
%% ------------------------------------------------------------------------------------ %%

@@

    We now investigate the performance of the PSF photometry in each of the five bands
    independently. 
    Fig \ref{fig:psf_mag} shows the difference between the input magnitude versus the
    \hscpipe{} \forced{} PSF magnitude ($\Delta \mathrm{mag}_{\mathrm{PSF}}$) as a 
    function of input magnitude. 
    We separate these stars into seven input magnitude bins.  
    In each bin, we characterize the statistical \textbf{precision} of the PSF 
    magnitude using the standard deviation of the distribution (\smag{}).
    Meanwhile, we characterize the statistical \textbf{accuracy} of the PSF magnitude 
    via the mean magnitude difference in each bin (\mmag{}). 
    This also informs us whether the PSF photometry is biased at certain input 
    magnitude.

@@

	Finally, we also perform similar tests for the \unforced{} PSF photometry in all 
	five bands, and find similar results. 
	To measure the \forced{} PSF photometry, \hscpipe{} fixes the centroid of the PSF 
	model across all five bands. 
	A difference between \forced{} and \unforced{} PSF magnitudes would therefore be 
	an indication of photometric uncertainties arising from inaccurate astrometric 
	calibrations and PSF modeling across different bands\footnote{On average, the 
	centroids are more accurate in \forced{} photometry as they are defined using 
	the band with higher \s2n{}}. 
	Fig \ref{fig:psf_diff} shows the difference between \forced{} and \unforced{} 
	PSF photometry for the $g$ and the $y$ band. 
	The overall differences are small ($<0.01$ mag). 
	At very faint end ($g_{\mathrm{Input}}>24.0$ mag and $y_{\mathrm{Input}}>23.5$,
	the \unforced{} photometry slightly overestimate the fluxes of stars comparing 
	to the \forced{} photometry.

@@

    The typical precision of $i$-band flux using \forced{} \cmodel{} is at 
    ${\sim}7-9$\% level in the \texttt{goodSeeing} \tract{} at 
    $i_{\mathrm{Input}}<24.0$ mag. 
    It moderately degrades to ${\sim}11$\% at $25.0$ mag. 
    The performance is similar in $i$ band for the \texttt{badSeeing} \tract{}. 
    At $20.0 < i_{\mathrm{Input}} < 25.0$ mag, the accuracies of \forced{} \cmodel{}
    magnitudes change from \plus{}$0.041$ mag to \minus{}$0.006$ mag, which suggest
    that \forced{} \cmodel{} photometry is unbiased down to the very faint end.

@@

    The precision of \forced{} \cmodel{} photometry is consistent across all filters.
    For the $g$, $r$, and $z$ bands, the statistical uncertainties are very similar to
    $i$-band results between $20.0$ and $25.0$ mag.
    The \forced{} \cmodel{} magnitudes are also unbiased for these three filters
    across the entire input magnitude range.
    The precision for the $y$ band is slightly worse, ranging from 9\% to 17\% in the
    same magnitude bins.
    In addition, the \forced{} \cmodel{} tends to overestimate the total flux in 
    the $y$ band at $>24.0$ mag. 
    This bias in the $y$ band flux is equal to \minus{}0.07 at $24.0$ mag to 
    \minus{}0.22 mag at 25.0 mag. 
    Worse seeing conditions and a higher background noise level mean that it is more
    difficult to detect faint objects in the $y$ band.
    At $y_{\mathrm{Input}}{\sim}24.0$, the average \s2n{} for \cmodel{} is already
    around the detection threshold.
